Functional trait data tell new story about biodiversity change

### 2021-02-11 paper/manuscript.Rmd
Flesh out intro

journal: "Ecography"
date: "`r Sys.Date()`"
bibliography: refs.bib
layout: 3p
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output: 
  rticles::elsevier_article:
    includes:
      in_header: preamble.tex
editor_options: 
  markdown: 
    wrap: 72
---

@@

Ecological communities are experiencing unprecedented change as a result
of anthropogenic pressures such as climate change, land use change, and
invasive species.

>>>>

journal: "Ecography"
date: "`r Sys.Date()`"
bibliography: refs.bib
layout: 3p
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output: 
  rticles::elsevier_article:
    includes:
     # in_header: preamble.tex
editor_options: 
  markdown: 
    wrap: 72
---

@@

Ecological communities are experiencing unprecedented change as a result
of anthropogenic pressures such as climate change, land use change, and
invasive species. Impacts of these pressures are well documented on a
global scale with an accelerating global extinction rate (citation) and
fundamental changes in some of the most well-known systems (e.g. coral
bleaching. At the local scale however the most common metric of
biodiversity, species richness, tells a different story. Recent
large-scale assessments of trends in biodiversity over time have shown a
decoupling of community composition from richness [@brose2016], evidence
of community-level regulation of richness [@gotelli2017], and no net
change in local biodiversity despite widespread environmental change
[@brown2001; @dornelas2014; @vellend2013;, @vellend2017] despite ongoing
species turnover. While communities are clearly changing, our most
common species-based approaches do not fully capture the nature of that
change.

Functional diversity offers a potentially powerful alternative for
detecting and describing community change by providing a mechanistic
link between the organisms in a system and the processes they perform
[@mcgill2006]. By summarizing functional traits rather than species,
functional diversity metrics capture the disproportionate impact of
losses or gains of functionally unique species. Functional diversity
metrics are particularly suited for understanding local-scale
biodiversity patterns as they can detect shifts in community structure
independent of species change. The rich history of connecting functional
diversity to ecosystem function and resilience and community assembly
provide further context in which to interpret changes in functional
diversity.
<!-- turn that last sentence into its own paragraph? e.g. what functional diversity tells us about community structure and function -->

Assessments of broad-scale temporal change in functional diversity have
previously been limited by a lack of functional trait data. The majority
of work has therefore focused largely on system-specific studies with
traits collected in situ. However, ongoing efforts to assemble
functional traits for a variety of taxa have made synthesis of existing
community assemblage data with functional traits possible for the first
time [@trindade-santos2020; @jarzyna2016; @barnagaud2017], providing
initial looks at how functional diversity changes on a broad-scale. We
approach local biodiversity change through this lens, providing the
first cross-taxa and cross-system assessment of functional diversity
change through time.
